Weak interspecific interactions in a sagebrush steppe: evidence from observations, models, and experiments

### 2018-01-22 removals/manuscript/removal_ms.tex
Complete set of new results with corrected demography data

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:32:17 2016
\begin{table}[ht]
\centering
\caption{Summary of posterior distributions for fixed effects for the \textit{A. tripartita} survival model. ``logarea" is the effect of plant size, ``Treatment*" is the removal effect, and the ``W.*" coefficients are effects of neighborhood crowding (the $\omega$s in eqn. \ref{eqn:survReg}). ``quant" refers to quantile and ``kld" reports the Kullback-Leibler divergence between the Gaussian and the (simplified) Laplace approximation to the marginal posterior densities. } 
\label{ARTRsurvival}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & -0.0207 & 0.2261 & -0.4554 & -0.0246 & 0.4367 & -0.0321 & 0.0000 \\ 
  logarea & 0.7208 & 0.0575 & 0.6109 & 0.7195 & 0.8378 & 0.7171 & 0.0000 \\ 
  TreatmentNo\_grass & -1.3218 & 0.7343 & -2.7293 & -1.3340 & 0.1563 & -1.3591 & 0.0000 \\ 
  W.ARTR & -1.5214 & 0.2075 & -1.9391 & -1.5179 & -1.1237 & -1.5107 & 0.0000 \\ 
  W.HECO & -0.0694 & 0.0423 & -0.1485 & -0.0708 & 0.0178 & -0.0738 & 0.0000 \\ 
  W.POSE & -0.0049 & 0.0761 & -0.1469 & -0.0077 & 0.1525 & -0.0134 & 0.0000 \\ 
  W.PSSP & 0.0281 & 0.0275 & -0.0235 & 0.0271 & 0.0849 & 0.0252 & 0.0000 \\ 
  W.allcov & -0.0055 & 0.0083 & -0.0219 & -0.0054 & 0.0109 & -0.0054 & 0.0000 \\ 
  W.allpts & 0.1694 & 0.1579 & -0.1386 & 0.1686 & 0.4812 & 0.1672 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:33:00 2016
\begin{table}[ht]
\centering
\caption{Summary of posterior distributions for fixed effects for the \textit{H. comata} survival model. See Table \ref{ARTRsurvival} for an explanation of coefficient names
and column headers.} 
\label{HECOsurvival}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 1.4189 & 0.2115 & 0.9991 & 1.4190 & 1.8371 & 1.4192 & 0.0000 \\ 
  logarea & 1.2885 & 0.0813 & 1.1399 & 1.2843 & 1.4601 & 1.2758 & 0.0000 \\ 
  TreatmentNo\_shrub & 0.3958 & 0.4175 & -0.4193 & 0.3942 & 1.2190 & 0.3909 & 0.0000 \\ 
  W.ARTR & -0.0064 & 0.0028 & -0.0120 & -0.0064 & -0.0009 & -0.0064 & 0.0000 \\ 
  W.HECO & -0.6647 & 0.0673 & -0.7996 & -0.6638 & -0.5351 & -0.6619 & 0.0000 \\ 
  W.POSE & 0.0732 & 0.0534 & -0.0304 & 0.0728 & 0.1790 & 0.0720 & 0.0000 \\ 
  W.PSSP & 0.0190 & 0.0184 & -0.0167 & 0.0188 & 0.0554 & 0.0185 & 0.0000 \\ 
  W.allcov & 0.0021 & 0.0047 & -0.0072 & 0.0021 & 0.0113 & 0.0021 & 0.0000 \\ 
  W.allpts & -0.1185 & 0.0919 & -0.2998 & -0.1183 & 0.0610 & -0.1177 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:34:30 2016
\begin{table}[ht]
\centering
\caption{Summary of posterior distributions for fixed effects for the \textit{P. secunda} survival model. See Table \ref{ARTRsurvival} for an explanation of coefficient names
and column headers.} 
\label{POSEsurvival}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 1.3162 & 0.1965 & 0.9242 & 1.3171 & 1.7024 & 1.3186 & 0.0000 \\ 
  logarea & 1.0585 & 0.0640 & 0.9365 & 1.0569 & 1.1902 & 1.0537 & 0.0000 \\ 
  TreatmentNo\_shrub & -0.2572 & 0.1723 & -0.5949 & -0.2573 & 0.0811 & -0.2576 & 0.0000 \\ 
  W.ARTR & 0.0001 & 0.0019 & -0.0036 & 0.0001 & 0.0038 & 0.0001 & 0.0000 \\ 
  W.HECO & -0.0153 & 0.0138 & -0.0424 & -0.0154 & 0.0119 & -0.0154 & 0.0000 \\ 
  W.POSE & -1.2632 & 0.0816 & -1.4260 & -1.2623 & -1.1053 & -1.2605 & 0.0000 \\ 
  W.PSSP & 0.0249 & 0.0122 & 0.0011 & 0.0249 & 0.0490 & 0.0247 & 0.0000 \\ 
  W.allcov & -0.0024 & 0.0026 & -0.0075 & -0.0024 & 0.0029 & -0.0024 & 0.0000 \\ 
  W.allpts & 0.0018 & 0.0524 & -0.1009 & 0.0018 & 0.1048 & 0.0017 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:35:48 2016
\begin{table}[ht]
\centering
\caption{Summary of posterior distributions for fixed effects for the \textit{P. spicata} survival model. See Table \ref{ARTRsurvival} for an explanation of coefficient names
and column headers.} 
\label{PSSPsurvival}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 1.2121 & 0.1699 & 0.8815 & 1.2103 & 1.5533 & 1.2066 & 0.0000 \\ 
  logarea & 1.5492 & 0.0976 & 1.3612 & 1.5474 & 1.7473 & 1.5437 & 0.0000 \\ 
  TreatmentNo\_shrub & -0.1885 & 0.2208 & -0.6237 & -0.1879 & 0.2431 & -0.1867 & 0.0000 \\ 
  W.ARTR & 0.0101 & 0.0021 & 0.0061 & 0.0101 & 0.0142 & 0.0101 & 0.0000 \\ 
  W.HECO & 0.0046 & 0.0185 & -0.0319 & 0.0046 & 0.0406 & 0.0047 & 0.0000 \\ 
  W.POSE & 0.0245 & 0.0384 & -0.0502 & 0.0242 & 0.1007 & 0.0236 & 0.0000 \\ 
  W.PSSP & -0.4430 & 0.0291 & -0.5010 & -0.4427 & -0.3867 & -0.4420 & 0.0000 \\ 
  W.allcov & 0.0100 & 0.0028 & 0.0046 & 0.0100 & 0.0155 & 0.0100 & 0.0000 \\ 
  W.allpts & 0.0943 & 0.0605 & -0.0246 & 0.0944 & 0.2129 & 0.0944 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:36:00 2016
\begin{table}[ht]
\centering
\caption{Summary of posterior distributions for fixed effects for the \textit{A. tripartita} growth model. ``logarea.t0" is the effect of plant size, ``Treatment*" is the removal effect, and the ``W.*" coefficients are effects of neighborhood crowding (the $\omega$s in eqn. \ref{eqn:growReg}. ``quant" refers to quantile and ``kld" reports the Kullback-Leibler divergence between the Gaussian and the (simplified) Laplace approximation to the marginal posterior densities.} 
\label{ARTRgrowth}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 0.7378 & 0.2437 & 0.2591 & 0.7378 & 1.2161 & 0.7377 & 0.0000 \\ 
  logarea.t0 & 0.8663 & 0.0393 & 0.7892 & 0.8663 & 0.9434 & 0.8663 & 0.0000 \\ 
  TreatmentNo\_grass & 0.1037 & 0.1436 & -0.1783 & 0.1037 & 0.3854 & 0.1037 & 0.0000 \\ 
  W.ARTR & -0.0364 & 0.0892 & -0.2116 & -0.0364 & 0.1387 & -0.0364 & 0.0000 \\ 
  W.HECO & 0.0033 & 0.0136 & -0.0233 & 0.0033 & 0.0299 & 0.0033 & 0.0000 \\ 
  W.POSE & -0.0573 & 0.0268 & -0.1100 & -0.0573 & -0.0047 & -0.0573 & 0.0000 \\ 
  W.PSSP & 0.0062 & 0.0084 & -0.0102 & 0.0062 & 0.0226 & 0.0062 & 0.0000 \\ 
  W.allcov & -0.0055 & 0.0030 & -0.0114 & -0.0055 & 0.0004 & -0.0055 & 0.0000 \\ 
  W.allpts & 0.0029 & 0.0477 & -0.0908 & 0.0029 & 0.0965 & 0.0029 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:36:24 2016
\begin{table}[ht]
\centering
\caption{Summary of posterior distributions for fixed effects for the \textit{H. comata} growth model. See Table \ref{ARTRgrowth} for an explanation of coefficient names
and column headers.} 
\label{HECOgrowth}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 0.3782 & 0.0797 & 0.2212 & 0.3783 & 0.5343 & 0.3784 & 0.0000 \\ 
  logarea.t0 & 0.8272 & 0.0205 & 0.7869 & 0.8272 & 0.8674 & 0.8272 & 0.0000 \\ 
  TreatmentNo\_shrub & -0.0162 & 0.1336 & -0.2785 & -0.0162 & 0.2460 & -0.0162 & 0.0000 \\ 
  W.ARTR & -0.0031 & 0.0010 & -0.0051 & -0.0031 & -0.0010 & -0.0031 & 0.0000 \\ 
  W.HECO & -0.0479 & 0.0195 & -0.0862 & -0.0479 & -0.0098 & -0.0479 & 0.0000 \\ 
  W.POSE & 0.0242 & 0.0162 & -0.0077 & 0.0242 & 0.0560 & 0.0242 & 0.0000 \\ 
  W.PSSP & -0.0151 & 0.0065 & -0.0279 & -0.0151 & -0.0023 & -0.0151 & 0.0000 \\ 
  W.allcov & -0.0038 & 0.0019 & -0.0076 & -0.0038 & 0.0000 & -0.0038 & 0.0000 \\ 
  W.allpts & -0.0513 & 0.0380 & -0.1258 & -0.0513 & 0.0232 & -0.0513 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:36:58 2016
\begin{table}[ht]
\centering
\caption{Summary of posterior distributions for fixed effects for the \textit{P. secunda} growth model. See Table \ref{ARTRgrowth} for an explanation of coefficient names
and column headers.} 
\label{POSEgrowth}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 0.4923 & 0.0681 & 0.3581 & 0.4923 & 0.6259 & 0.4924 & 0.0000 \\ 
  logarea.t0 & 0.6750 & 0.0232 & 0.6292 & 0.6750 & 0.7203 & 0.6751 & 0.0000 \\ 
  TreatmentNo\_shrub & 0.2161 & 0.0644 & 0.0897 & 0.2161 & 0.3425 & 0.2161 & 0.0000 \\ 
  W.ARTR & -0.0002 & 0.0008 & -0.0019 & -0.0002 & 0.0014 & -0.0002 & 0.0000 \\ 
  W.HECO & 0.0039 & 0.0063 & -0.0084 & 0.0039 & 0.0161 & 0.0039 & 0.0000 \\ 
  W.POSE & -0.2641 & 0.0387 & -0.3400 & -0.2641 & -0.1883 & -0.2641 & 0.0000 \\ 
  W.PSSP & -0.0073 & 0.0056 & -0.0183 & -0.0073 & 0.0038 & -0.0073 & 0.0000 \\ 
  W.allcov & -0.0003 & 0.0012 & -0.0026 & -0.0003 & 0.0020 & -0.0003 & 0.0000 \\ 
  W.allpts & -0.0254 & 0.0231 & -0.0709 & -0.0254 & 0.0200 & -0.0254 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:37:48 2016
\begin{table}[ht]
\centering
\caption{Summary of posterior distributions for fixed effects for the \textit{P. spicata} growth model. See Table \ref{ARTRgrowth} for an explanation of coefficient names
and column headers.} 
\label{PSSPgrowth}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 0.3987 & 0.0660 & 0.2690 & 0.3987 & 0.5281 & 0.3988 & 0.0000 \\ 
  logarea.t0 & 0.8249 & 0.0149 & 0.7956 & 0.8249 & 0.8543 & 0.8249 & 0.0000 \\ 
  TreatmentNo\_shrub & 0.1948 & 0.0714 & 0.0546 & 0.1948 & 0.3349 & 0.1948 & 0.0000 \\ 
  W.ARTR & -0.0025 & 0.0008 & -0.0041 & -0.0025 & -0.0010 & -0.0025 & 0.0000 \\ 
  W.HECO & -0.0118 & 0.0072 & -0.0260 & -0.0118 & 0.0023 & -0.0118 & 0.0000 \\ 
  W.POSE & -0.0067 & 0.0130 & -0.0323 & -0.0067 & 0.0189 & -0.0067 & 0.0000 \\ 
  W.PSSP & -0.1480 & 0.0133 & -0.1740 & -0.1480 & -0.1220 & -0.1480 & 0.0000 \\ 
  W.allcov & -0.0036 & 0.0011 & -0.0057 & -0.0036 & -0.0015 & -0.0036 & 0.0000 \\ 
  W.allpts & -0.0522 & 0.0236 & -0.0984 & -0.0522 & -0.0060 & -0.0522 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Summary of fixed effects for the \textit{P. secunda} growth model with individual-level \textit{A. tripartita removal} data (the ``inARTR" coefficient). See Table \ref{ARTRgrowth} for an explanation of other coefficient names and column headers. } 
\label{table:POSEgrowth-inARTR}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 0.4932 & 0.0622 & 0.3700 & 0.4934 & 0.6154 & 0.4937 & 0.0000 \\ 
  logarea.t0 & 0.6746 & 0.0220 & 0.6306 & 0.6747 & 0.7177 & 0.6750 & 0.0000 \\ 
  TreatmentNo\_shrub & 0.2370 & 0.0739 & 0.0919 & 0.2370 & 0.3820 & 0.2370 & 0.0000 \\ 
  W.ARTR & -0.0002 & 0.0008 & -0.0018 & -0.0002 & 0.0014 & -0.0002 & 0.0000 \\ 
  W.HECO & 0.0038 & 0.0062 & -0.0083 & 0.0038 & 0.0160 & 0.0038 & 0.0000 \\ 
  W.POSE & -0.2644 & 0.0383 & -0.3395 & -0.2644 & -0.1893 & -0.2644 & 0.0000 \\ 
  W.PSSP & -0.0075 & 0.0056 & -0.0184 & -0.0075 & 0.0034 & -0.0075 & 0.0000 \\ 
  W.allcov & -0.0003 & 0.0012 & -0.0026 & -0.0003 & 0.0020 & -0.0003 & 0.0000 \\ 
  W.allpts & -0.0258 & 0.0229 & -0.0707 & -0.0258 & 0.0191 & -0.0258 & 0.0000 \\ 
  inARTR & -0.0592 & 0.1133 & -0.2817 & -0.0592 & 0.1632 & -0.0592 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:32:17 2016
\begin{table}[ht]
\centering
\caption{Summary of posterior distributions for fixed effects for the \textit{A. tripartita} survival model. ``logarea" is the effect of plant size, ``Treatment*" is the removal effect, and the ``W.*" coefficients are effects of neighborhood crowding (the $\omega$s in eqn. \ref{eqn:survReg}). ``quant" refers to quantile and ``kld" reports the Kullback-Leibler divergence between the Gaussian and the (simplified) Laplace approximation to the marginal posterior densities. } 
\label{ARTRsurvival}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & -0.2613 & 0.1344 & -0.5276 & -0.2605 & 0.0001 & -0.2588 & 0.0000 \\ 
  logarea & 0.7093 & 0.0400 & 0.6315 & 0.7090 & 0.7885 & 0.7085 & 0.0000 \\ 
  TreatmentNo\_grass & -0.9994 & 0.6453 & -2.2156 & -1.0182 & 0.3228 & -1.0565 & 0.0000 \\ 
  W.ARTR & -2.8522 & 0.4187 & -3.6968 & -2.8443 & -2.0513 & -2.8284 & 0.0000 \\ 
  W.HECO & -0.0720 & 0.0615 & -0.1856 & -0.0747 & 0.0565 & -0.0804 & 0.0000 \\ 
  W.POSE & 0.0617 & 0.0895 & -0.1061 & 0.0588 & 0.2459 & 0.0528 & 0.0000 \\ 
  W.PSSP & 0.0387 & 0.0475 & -0.0500 & 0.0370 & 0.1369 & 0.0335 & 0.0000 \\ 
  W.allcov & -0.0065 & 0.0109 & -0.0282 & -0.0065 & 0.0148 & -0.0063 & 0.0000 \\ 
  W.allpts & 0.1293 & 0.1653 & -0.1956 & 0.1294 & 0.4533 & 0.1296 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:33:00 2016
\begin{table}[ht]
\centering
\caption{Summary of posterior distributions for fixed effects for the \textit{H. comata} survival model. See Table \ref{ARTRsurvival} for an explanation of coefficient names
and column headers.} 
\label{HECOsurvival}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 1.4753 & 0.2011 & 1.0764 & 1.4753 & 1.8736 & 1.4753 & 0.0000 \\ 
  logarea & 1.1991 & 0.0747 & 1.0622 & 1.1954 & 1.3561 & 1.1874 & 0.0000 \\ 
  TreatmentNo\_shrub & 0.2915 & 0.3900 & -0.4693 & 0.2898 & 1.0610 & 0.2864 & 0.0000 \\ 
  W.ARTR & -0.0063 & 0.0030 & -0.0121 & -0.0063 & -0.0005 & -0.0063 & 0.0000 \\ 
  W.HECO & -1.6962 & 0.1458 & -1.9894 & -1.6939 & -1.4163 & -1.6891 & 0.0000 \\ 
  W.POSE & 0.0649 & 0.0563 & -0.0442 & 0.0644 & 0.1768 & 0.0634 & 0.0000 \\ 
  W.PSSP & 0.0313 & 0.0360 & -0.0381 & 0.0309 & 0.1031 & 0.0301 & 0.0000 \\ 
  W.allcov & -0.0012 & 0.0062 & -0.0135 & -0.0012 & 0.0110 & -0.0012 & 0.0000 \\ 
  W.allpts & -0.1295 & 0.1004 & -0.3273 & -0.1293 & 0.0670 & -0.1290 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:34:30 2016
\begin{table}[ht]
\centering
\caption{Summary of posterior distributions for fixed effects for the \textit{P. secunda} survival model. See Table \ref{ARTRsurvival} for an explanation of coefficient names
and column headers.} 
\label{POSEsurvival}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 1.4020 & 0.1922 & 1.0176 & 1.4031 & 1.7793 & 1.4050 & 0.0000 \\ 
  logarea & 1.0362 & 0.0645 & 0.9139 & 1.0343 & 1.1696 & 1.0307 & 0.0000 \\ 
  TreatmentNo\_shrub & -0.1604 & 0.1622 & -0.4784 & -0.1606 & 0.1583 & -0.1610 & 0.0000 \\ 
  W.ARTR & 0.0000 & 0.0020 & -0.0038 & 0.0000 & 0.0039 & -0.0000 & 0.0000 \\ 
  W.HECO & -0.0224 & 0.0208 & -0.0631 & -0.0225 & 0.0185 & -0.0227 & 0.0000 \\ 
  W.POSE & -2.0073 & 0.1112 & -2.2290 & -2.0062 & -1.7921 & -2.0038 & 0.0000 \\ 
  W.PSSP & 0.0468 & 0.0238 & 0.0004 & 0.0466 & 0.0939 & 0.0463 & 0.0000 \\ 
  W.allcov & -0.0061 & 0.0035 & -0.0130 & -0.0061 & 0.0008 & -0.0061 & 0.0000 \\ 
  W.allpts & -0.0383 & 0.0567 & -0.1494 & -0.0384 & 0.0730 & -0.0385 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:35:48 2016
\begin{table}[ht]
\centering
\caption{Summary of posterior distributions for fixed effects for the \textit{P. spicata} survival model. See Table \ref{ARTRsurvival} for an explanation of coefficient names
and column headers.} 
\label{PSSPsurvival}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 1.1978 & 0.1639 & 0.8783 & 1.1962 & 1.5257 & 1.1933 & 0.0000 \\ 
  logarea & 1.5138 & 0.0935 & 1.3336 & 1.5122 & 1.7029 & 1.5092 & 0.0000 \\ 
  TreatmentNo\_shrub & -0.2466 & 0.2023 & -0.6454 & -0.2460 & 0.1489 & -0.2449 & 0.0000 \\ 
  W.ARTR & 0.0099 & 0.0022 & 0.0057 & 0.0099 & 0.0142 & 0.0099 & 0.0000 \\ 
  W.HECO & 0.0025 & 0.0289 & -0.0550 & 0.0028 & 0.0586 & 0.0032 & 0.0000 \\ 
  W.POSE & 0.0517 & 0.0389 & -0.0222 & 0.0508 & 0.1308 & 0.0490 & 0.0000 \\ 
  W.PSSP & -1.1267 & 0.0739 & -1.2743 & -1.1258 & -0.9838 & -1.1242 & 0.0000 \\ 
  W.allcov & 0.0131 & 0.0037 & 0.0060 & 0.0131 & 0.0203 & 0.0131 & 0.0000 \\ 
  W.allpts & 0.0756 & 0.0658 & -0.0540 & 0.0757 & 0.2045 & 0.0760 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:36:00 2016
\begin{table}[ht]
\centering
\caption{Summary of posterior distributions for fixed effects for the \textit{A. tripartita} growth model. ``logarea.t0" is the effect of plant size, ``Treatment*" is the removal effect, and the ``W.*" coefficients are effects of neighborhood crowding (the $\omega$s in eqn. \ref{eqn:growReg}. ``quant" refers to quantile and ``kld" reports the Kullback-Leibler divergence between the Gaussian and the (simplified) Laplace approximation to the marginal posterior densities.} 
\label{ARTRgrowth}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 0.7092 & 0.2385 & 0.2396 & 0.7091 & 1.1784 & 0.7090 & 0.0000 \\ 
  logarea.t0 & 0.8689 & 0.0394 & 0.7912 & 0.8689 & 0.9466 & 0.8689 & 0.0000 \\ 
  TreatmentNo\_grass & 0.1385 & 0.1446 & -0.1453 & 0.1385 & 0.4221 & 0.1385 & 0.0000 \\ 
  W.ARTR & -0.1497 & 0.1960 & -0.5345 & -0.1497 & 0.2347 & -0.1497 & 0.0000 \\ 
  W.HECO & 0.0045 & 0.0198 & -0.0343 & 0.0045 & 0.0433 & 0.0045 & 0.0000 \\ 
  W.POSE & -0.0614 & 0.0308 & -0.1218 & -0.0614 & -0.0010 & -0.0614 & 0.0000 \\ 
  W.PSSP & -0.0050 & 0.0158 & -0.0360 & -0.0050 & 0.0260 & -0.0050 & 0.0000 \\ 
  W.allcov & -0.0052 & 0.0041 & -0.0133 & -0.0052 & 0.0029 & -0.0052 & 0.0000 \\ 
  W.allpts & 0.0115 & 0.0536 & -0.0938 & 0.0115 & 0.1167 & 0.0115 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:36:24 2016
\begin{table}[ht]
\centering
\caption{Summary of posterior distributions for fixed effects for the \textit{H. comata} growth model. See Table \ref{ARTRgrowth} for an explanation of coefficient names
and column headers.} 
\label{HECOgrowth}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 0.3937 & 0.0815 & 0.2330 & 0.3938 & 0.5537 & 0.3940 & 0.0000 \\ 
  logarea.t0 & 0.8207 & 0.0213 & 0.7788 & 0.8207 & 0.8626 & 0.8207 & 0.0000 \\ 
  TreatmentNo\_shrub & 0.0691 & 0.1314 & -0.1891 & 0.0691 & 0.3268 & 0.0691 & 0.0000 \\ 
  W.ARTR & -0.0042 & 0.0011 & -0.0063 & -0.0042 & -0.0020 & -0.0042 & 0.0000 \\ 
  W.HECO & -0.2134 & 0.0618 & -0.3348 & -0.2134 & -0.0922 & -0.2135 & 0.0000 \\ 
  W.POSE & 0.0204 & 0.0178 & -0.0146 & 0.0204 & 0.0553 & 0.0204 & 0.0000 \\ 
  W.PSSP & -0.0373 & 0.0131 & -0.0630 & -0.0373 & -0.0117 & -0.0373 & 0.0000 \\ 
  W.allcov & -0.0062 & 0.0027 & -0.0115 & -0.0062 & -0.0010 & -0.0062 & 0.0000 \\ 
  W.allpts & -0.0212 & 0.0416 & -0.1028 & -0.0212 & 0.0604 & -0.0212 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:36:58 2016
\begin{table}[ht]
\centering
\caption{Summary of posterior distributions for fixed effects for the \textit{Poa secunda} growth model. See Table \ref{ARTRgrowth} for an explanation of coefficient names
and column headers.} 
\label{POSEgrowth}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 0.5069 & 0.0625 & 0.3830 & 0.5070 & 0.6299 & 0.5072 & 0.0000 \\ 
  logarea.t0 & 0.6669 & 0.0228 & 0.6215 & 0.6670 & 0.7116 & 0.6673 & 0.0000 \\ 
  TreatmentNo\_shrub & 0.1937 & 0.0632 & 0.0696 & 0.1937 & 0.3176 & 0.1937 & 0.0000 \\ 
  W.ARTR & -0.0004 & 0.0009 & -0.0022 & -0.0004 & 0.0013 & -0.0004 & 0.0000 \\ 
  W.HECO & 0.0110 & 0.0100 & -0.0087 & 0.0110 & 0.0307 & 0.0110 & 0.0000 \\ 
  W.POSE & -0.5753 & 0.0623 & -0.6977 & -0.5753 & -0.4530 & -0.5753 & 0.0000 \\ 
  W.PSSP & -0.0093 & 0.0114 & -0.0316 & -0.0093 & 0.0130 & -0.0093 & 0.0000 \\ 
  W.allcov & -0.0004 & 0.0016 & -0.0035 & -0.0004 & 0.0028 & -0.0004 & 0.0000 \\ 
  W.allpts & -0.0340 & 0.0255 & -0.0842 & -0.0340 & 0.0161 & -0.0340 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:37:48 2016
\begin{table}[ht]
\centering
\caption{Summary of posterior distributions for fixed effects for the \textit{P. spicata} growth model. See Table \ref{ARTRgrowth} for an explanation of coefficient names
and column headers.} 
\label{PSSPgrowth}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 0.3846 & 0.0710 & 0.2425 & 0.3851 & 0.5236 & 0.3858 & 0.0000 \\ 
  logarea.t0 & 0.8259 & 0.0167 & 0.7929 & 0.8259 & 0.8587 & 0.8260 & 0.0000 \\ 
  TreatmentNo\_shrub & 0.2262 & 0.0681 & 0.0924 & 0.2262 & 0.3598 & 0.2262 & 0.0000 \\ 
  W.ARTR & -0.0023 & 0.0008 & -0.0038 & -0.0023 & -0.0007 & -0.0023 & 0.0000 \\ 
  W.HECO & -0.0201 & 0.0111 & -0.0419 & -0.0201 & 0.0017 & -0.0201 & 0.0000 \\ 
  W.POSE & -0.0200 & 0.0137 & -0.0469 & -0.0200 & 0.0069 & -0.0200 & 0.0000 \\ 
  W.PSSP & -0.3845 & 0.0335 & -0.4502 & -0.3845 & -0.3188 & -0.3846 & 0.0000 \\ 
  W.allcov & -0.0048 & 0.0014 & -0.0076 & -0.0048 & -0.0021 & -0.0048 & 0.0000 \\ 
  W.allpts & -0.0510 & 0.0256 & -0.1012 & -0.0510 & -0.0008 & -0.0510 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Summary of fixed effects for the \textit{P. secunda} growth model with individual-level \textit{A. tripartita removal} data (the ``inARTR" coefficient). See Table \ref{ARTRgrowth} for an explanation of other coefficient names and column headers. } 
\label{table:POSEgrowth-inARTR}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 0.5080 & 0.0625 & 0.3841 & 0.5081 & 0.6311 & 0.5084 & 0.0000 \\ 
  logarea.t0 & 0.6665 & 0.0228 & 0.6211 & 0.6666 & 0.7111 & 0.6669 & 0.0000 \\ 
  TreatmentNo\_shrub & 0.2247 & 0.0744 & 0.0786 & 0.2247 & 0.3707 & 0.2247 & 0.0000 \\ 
  W.ARTR & -0.0004 & 0.0009 & -0.0022 & -0.0004 & 0.0013 & -0.0004 & 0.0000 \\ 
  W.HECO & 0.0109 & 0.0100 & -0.0088 & 0.0109 & 0.0306 & 0.0109 & 0.0000 \\ 
  W.POSE & -0.5770 & 0.0624 & -0.6995 & -0.5770 & -0.4547 & -0.5770 & 0.0000 \\ 
  W.PSSP & -0.0093 & 0.0114 & -0.0316 & -0.0093 & 0.0130 & -0.0093 & 0.0000 \\ 
  W.allcov & -0.0004 & 0.0016 & -0.0036 & -0.0004 & 0.0027 & -0.0004 & 0.0000 \\ 
  W.allpts & -0.0340 & 0.0256 & -0.0842 & -0.0340 & 0.0161 & -0.0340 & 0.0000 \\ 
  inARTR & -0.0890 & 0.1126 & -0.3100 & -0.0890 & 0.1319 & -0.0890 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}
